Network packet generation for Artificial Intelligence\\

### 2020-02-27 paper1/paper1.tex
Extended abstract and introduction

\begin{abstract}
Supervised learning in artificial intelligence requires a training dataset that is already labeled. Doing so with network packets is a challenge due to the fact that even Intrusion Detection Systems are not always correct with their guessing. To overcome this problem it is necessary to generate malicious and benign packets and label them accordingly. To increase the quality of the dataset the IP addresses from the machines should not remain the same for all of the data and the malicious and benign traffic should be mixed.

\end{abstract}

@@

At this point all of our considerations are based on theoretical research without practical implementation which will come to life in further work. Therefore this paper sets a direction and foundation for the next steps and shows possible solutions at a high level.

@@

\section{Further research}
Future work on this topic could try to look at attack methods on a more detailed level in order to provide specific information. Furthermore, it makes sense to identify additional tools for carrying out cyber-attacks. There is also room for further research in the search for other ways of generating realistic network traffic including benign and malicious behavior.

>>>>

\begin{abstract}
Supervised learning in artificial intelligence requires a training dataset that is already labeled. Doing so with network packets is a challenge due to the fact that even Intrusion Detection Systems are not always correct with their guessing. To overcome this problem it is necessary to generate malicious and benign packets and label them accordingly. To increase the quality of the dataset the IP addresses from the machines should not remain the same for all of the data and the malicious and benign traffic should be mixed. Therefore, a literature search is carried out in the relevant specialist literature, scientific work and publications in order to research the necessary basics. Different types of attacks, tools for carrying out attacks and how realistic network traffic can be generated are to be determined. The results show that some approaches exist to divide the multitude of different attack methods into a few, individual groups. Nine generic attack classes as well as typical attack targets and vulnerabilities are identified. In addition, various tools for carrying out attacks are determined. These can be divided into the areas of information gathering and attack launching. Furthermore, different strategies are considered to generate realistic network traffic consisting of benign and malicious data packets. In conclusion, the information determined in the context of this work helps to generate an appropriate dataset for supervised machine learning.
\end{abstract}

@@

At this point all of our considerations are based on theoretical research without practical implementation which will come to life in further work. Therefore this paper sets a direction and foundation for the next steps and shows possible solutions at a high level. The results are elaborated on the basis of an extensive literature search in relevant specialist literature, scientific works and publications. The list of individual sources can be found at the end of the work.

@@

\section{Further research}
Future work on this topic could try to look at attack methods on a more detailed level in order to provide more specific information. Furthermore, it makes sense to identify additional tools for carrying out cyber-attacks. There is also room for further research in the search for other ways of generating realistic network traffic including benign and malicious behavior.
